---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Homework6
[![R-CMD-check](https://github.com/vramanathan2005/Homework6/actions/workflows/check-standard.yaml/badge.svg)](https://github.com/vramanathan2005/Homework6/actions/workflows/R-CMD-check.yaml)

The **Homework6** package implements an S4 class called `sparse_numeric` for working with sparse numeric vectors in R.
Instead of storing every element of a vector, it stores only the non-zero values and their positions, which is more
memory-efficient for large, mostly-zero vectors.

The package provides:

- The `sparse_numeric` S4 class (with slots `value`, `pos`, and `length`)
- Coercion between base `numeric` vectors and `sparse_numeric`
- Arithmetic operations for sparse vectors: `+`, `-`, `*`
- `sparse_crossprod()` for dot products
- A `mean()` method that correctly includes implicit zeros
- A `norm()` method for the Euclidean (L2) norm
- `standardize()` to z-score a sparse vector (mean 0, sd 1)

## Installation

You can install the development version of **Homework6** from GitHub:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("vramanathan2005/Homework6")
```

## Basic example

The example below shows how to create a sparse vector, compute its mean and norm,
and standardize it:

```{r}
library(Homework6)

# start with a dense numeric vector
x_dense <- c(0, 5, 0, -2, 0, 3)

# convert to sparse_numeric
x_sparse <- as(x_dense, "sparse_numeric")

# look at the sparse representation and dense version
x_sparse
as(x_sparse, "numeric")
```

```{r}
# summary functions
mean_x   <- mean(x_sparse)   # includes implicit zeros
norm_x   <- norm(x_sparse)   # Euclidean norm

x_std    <- standardize(x_sparse)
x_std_dn <- as(x_std, "numeric")

mean_x
norm_x
x_std_dn
mean(x_std_dn)
sd(x_std_dn)
```
